Parameteric controls on responses to biogeochemical forcing in the CLM5

### 2018-11-29 main.tex
Updates from ShareLaTeX

\begin{document}
%tentative author list...
\authors{Rosie Fisher\affil{1},
William Wieder\affil{1},
Benjamin Sanderson\affil{2},
Charles Koven\affil{3},
Keith Oleson\affil{1},
Chonggang Xu\affil{4},
Joshua Fisher\affil{5},
Mingjie Shi\affil{5},
Anthony Walker\affil{6},
Gordon Bonan\affil{1},
David M. Lawrence\affil{1}
}

@@

\affiliation{2}{CERFACS, Toulouse, France}

\affiliation{3}{Lawrence Berkeley National Laboratory, Berkeley, California, USA}

\affiliation{4}{Los Alamos National Laboratory, Los Alamos, New Mexico, USA}

\affiliation{5}{NASA Jet Propulsion Laboratory, Pasadena, California, USA}

\affiliation{6}{Oak Ridge National Laboratory, Oak Ridge, Tennessee, USA}

@@

\begin{keypoints}

\item A suite of modifications to the Nitrogen cycle representation were added to the Community Land Model, version 5 (CLM5).

\item New features of the N model include prognostic $V_{c,max}$ and $J_{max}$, representation of the carbon economic cost of Nitrogen uptake, switching of N uptake between alternative sources, variable tissue C:N ratios and dynamic leaf resorption of Nitrogen.

\item Here we assess the sensitivity of the model to a suite of parameters pertinent to the cycling of Carbon and Nitrogen. We assess the dependence of the both the model state, and also the responses of the system to CO$_{2}$ and Nitrogen fertilization to parametric uncertainty. Model runs are conducted at representative individual sites in temperate, tropical and boreal systems.

\item The model responses to CO$_{2}$  and N fertilization are primarily linked to the representation of the fraction of plants that can fix Nitrogen, the costs of N in the environment and stoichiometric flexibility of plant tissues, all of which are subject to large empirical and theoretical uncertainty.

\item Identification of the primary factors driving ecosystem responses to fertilization both assists in the interpretation of global simulations and in the identification of priorities for fieldwork and process updates.
\end{keypoints}

\section{Introduction}

Simulating the cycling of nutrients, and how nutrient availability impacts ecosystem growth and function, has been repeatedly identified as a crucial element of Earth system models (\cite{piao2013}, \cite{gruber2008}, \cite{wang2009}). In the CMIP5 multi-model inter-comparison process, only one model, the Community Land Model v4.0, included an active nitrogen (N) cycle. The CLM4.0 projected that inclusion of N dynamics might significantly limit the ability of the terrestrial biosphere to respond to fertilization by increasing atmospheric carbon dioxide (\cite{friedlingstein2006}, \cite{friedlingstein2014}, \cite{arora2013}). Subsequent and parallel to CMIP5, many terrestrial biosphere and land surface models that represent global N dynamics using alternative structural assumptions have been developed (\cite{wang2007}, \cite{zaehle2010}, \cite{goll2012}, \cite{smith2014}). Nonetheless, substantial uncertainty remains in the land surface modeling community regarding how nutrient limitations should be represented in models (\cite{zaehle2011}).

@@

The Community Land Model is the land surface representation within the Community Earth System Model (CESM, \cite{hurrell2013}). Version 5 of the CLM was recently released to the research community as part of the CESM2.0 release and open-source releases and development are housed at \url{https://github.com/ESCOMP/ctsm/}. An overview of model developments is presented by \cite{lawrence2018}, a description of the global Nitrogen cycling by Wieder et al. (in prep), the crop model by(Lombardozzi et al. in prep), the land use components by (Lawrence P et al. in prep), and plant hydraulics by (Kennedy et al., 2018).

CLM5 includes numerous major updates of the nitrogen cycle representation relative to CLM4.0 and CLM4.5. The introduction of several new dynamical features into the CLM5 has implications for both parameteric uncertainty and responses to environmental forcing. Wieder et al. (in prep) report the global-scale carbon cycle implications of the full model update and note that the CLM5 carbon uptake responds more strongly to CO$_{2}$ and less strongly to N fertilization than its predecessors.  In this paper, we describe the new components of the biogeochemical cycling, and investigate the features of the new model that control the model state and biogeochemical forcing responses in depth, using single-site experiments and parametric sensitivity analyses.

\subsection{Model Updates}

The CLM5 nitrogen cycling builds on the implementation of carbon-nitrogen interactions in the CLM4.0(CN) model (\cite{thornton2007}), and on modifications to the biogeochemical cycling (notably vertically stratified soil decomposition processes) included in the CLM4.5 (\cite{koven2013}, \cite{bonan2012}). The new model integrates three major additional prognostic elements of the Nitrogen cycle, including: \\

1) The `LUNA' model (Leaf Utilization of Nitrogen for Assimilation), which simulates distribution of N between different leaf assimilation processes (\cite{xu2012}, \cite{ali2016}) \\

@@

3) The `FLEXCN' N cycle implementation, adapted from \cite{ghimire2016}, which is used in CLM5 primarily to allow variation in tissue C:N ratios,  .\\

@@

The LUNA model predicts the optimal balance of of $V_{c,max}$ and $J_{max}$ for the prevailing time-averaged environmental conditions. The model determines the rate constants that are consistent with a co-limitation of photosynthesis by both electron capture and carboxylation processes. In this fashion, $V_{c,max}$ is primarily controlled by the N per unit leaf area $N_{area}$, (which is itself a function of the target C/N ratio, the specific leaf area, and the prognostic variation in leaf C/N ratios) and prevailing environmental conditions (CO$_{2}$, temperature, humidity, soil moisture). The capacity of the LUNA model to represent appropriate responses to temperature and CO$_{2}$ was assessed by \cite{xu2012} while the global calibration and the geographical predictions of the model were described by \cite{ali2016}.

\subsubsection{FUN}

Under circumstances where insufficient N exists to match all of the carbon assimilated for a given C:N ratio, the CLM4.0 model reduced the gross photosynthetic flux down to the level at which growth could be supported by the assimilated N. This process occurred after the calculation of stomatal conductance (which is linked to assimilation rates via the Ball-Berry model) and therefore created inconsistencies between C assimilation and water cycling, especially under conditions of N limitation, as discussed extensively in the literature (\cite{medlyn2011}, \cite{bonan2012}, \cite{dekauwe2014}, \cite{walker2014}).

One major issue confronting N cycle models is how to deal with this 'excess' carbon under N limiting conditions (\cite{zaehle2010}, \cite{dekauwe2014}). The FUN model operates on the principle that for the alternative sources of nitrogen acquisition by plants (active uptake from soil, retranslocation from senescent tissues, and symbiotic N fixation) there is a concurrent cost in terms of carbon. Further, the cost of each uptake pathway is variable in both time and space. FUN hypothesizes that plants will take up Nitrogen from pathways which are 'cheaper' to them. Where N is scarce in the environment, carbon that would otherwise have been used for plant growth can be deployed to acquire (pay for) more N. Thus, N limitation leads to reduced growth and higher expenditure of C on N uptake (and reduces carbon use efficiency).  The central element of FUN is a set of simultaneous equations which assume, firstly, that the total carbon available (after maintenance respiration and replenishment of stores are accounted for), `$C_{avail}$', is either used for plant growth ($C_{growth}$) or for nitrogen uptake, ($C_{nuptake}$).

\begin{equation}
C_{growth}=C_{avail}+C_{nuptake}
\end{equation}

Further, the nitrogen acquired from the environment ($N_{uptake}$) must equal the amount spent on N divided by it's average cost ($N_{cost}$), and also the amount of carbon deployed for growth divided by the plant CN ratio:

@@

\begin{equation}
C_{nuptake} =\frac{C_{avail}}{ ( (1.0+f_{gr})*(CN_{target} / N_{cost}) + 1) }
\end{equation}

The average Nitrogen cost ($N_{cost}$) is derived from the uptake of N, weighted for it's cost across all uptake streams, while the plant CN ratio ($CN_{plant}$) is the combined target CN ratio of all the plant tissues, weighted for the size of the different pools. The FUN model is documented at \url{https://escomp.github.io/ctsm-docs/doc/build/html/tech_note/FUN/CLM50_Tech_Note_FUN.html}

One issue addressed by FUN is the preferential use of symbiotic N fixation when soil mineral N concentrations are low (\cite{vitousek2002}). The CLM4.0 and CLM4.5 predict N fixation as a linear function of net primary productivity ((\cite{wieder2015} illustrated the impacts of uncertainty in this function).  FUN considers fixation rates to be an emergent property of plant assimilation rates, the relative costs of environmental N acquisition compared to fixation, and temperature (which exerts a primary control over the enzymatic processes, following \cite{houlton2008}). Fixation is preferred when the costs of `active' N acquisition from soil are higher than that of fixation. Note that while the CLM5 has no representation of biological succession (\cite{fisher2018}), this property nonetheless affects the amount of time taken to achieve a spun-up state from bare ground. In most cases, N fixation is preferred when soil N is low, and so soil N builds up quickly. In low productivity areas, however, carbon is required to fix N from a 'cold start' initial state, impacting the carbon use efficiency and survival of marginal plants; thus higher initial stocks of N are required to allow growth once metabolic and turnover costs have been met in early spin-up.

\subsubsection{FLEXCN}
The results of FACE model-data comparison exercises illustrated that changes in the C:N ratio accounted for large changes in ecosystem carbon storage under elevated CO$_{2}$ (\cite{zaehle2014}, \cite{medlyn2015using}).  These changes were not captured by the static tissue C:N ratios used in the CLM4.0 and CLM4.5 nitrogen cycle. For this reason, we introduce a flexible tissue C:N ratio into the CLM5.

\cite{ghimire2016} implemented a suite of modifications to the CLM Nitrogen cycling model, including variable tissue C:N ratio, prognostic $V_{c,max}$ (resulting from this dynamic leaf N content) and also an alternative Nitrogen uptake algorithm. In the default configuration of CLM5, the LUNA model predicts $V_{c,max}$ from leaf N content (while also taking into account environmental conditions), and the FUN model represents Nitrogen uptake, thus the primary element of CLM5 utilized from the \cite{ghimire2016} model is the modification to the allocation scheme that allows tissue C:N ratios to be modified in response to varying supply of Nitrogen. In the new allocation algorithm, the total Nitrogen supply in each timestep is partitioned between tissues according to their relative 'demand' terms (ascertained from the target C:N ratio and the carbon allocated to the pool) and C:N ratios vary with Nitrogen supply rates.  The allocation scheme retains a fixed-fraction approach to allocation in general, and thus is capable of generating physiologically sub-optimal leaf area index values, for example, with some of the canopy in negative carbon balance, an issue which must be taken into account during simulations under high productivity conditions.

\subsubsection{Adaptation of FUN to flexible CN ratios}

The FUN model was originally conceived with a static tissue C:N ratio, and will by default allocated an amount of carbon to N uptake that will exactly track the target C:N ratio. In CLM5, one of the aims of the development process was to incorporate a varying C:N ratio. To that end, it is necessary to modify the amount of Carbon expended on N uptake (and thus the amount of N required). The degree to which tissue C:N content varies as N becomes limiting in unclear in the literature, and N cycle models typically include heuristic representations of tissue N adjustments under N limited conditions (including \cite{zaehle2010},\cite{ghimire2016}). Here we include a placeholder algorithm that adapts to 1) the environmental cost of N acquisition and 2) the degree to which the plant is already far from it's target N content. When N is expensive in the environment, less C is spent on uptake, increasing C:N ratios where N is scarce. When plants become extremely N limited, however, expenditure increases again to prevent CN ratios becoming unrealistically high. This new algorithm is also documented in the CLM5 technical description ((\url{(https://escomp.github.io/ctsm-docs/doc/build/html/tech_note/index.html)}) and includes three tuning parameters ($flexcn_{a}$, $flexcn_{b}$ \& $flexcn_{c}$) the sensitivity of which is investigated here.

\subsection{Content of this paper}

In this paper, we assess in detail the sensitivity of the CLM5 model structure to its input parameters. We use a range of single site experiments, combined with one-at-a-time parameter uncertainty analyses from the default state, as well as CO$_{2}$ fertilization experiments and Nitrogen addition experiments, 
to fully investigate the performance of the model under steady-state and step-change modifications in forcing.

Given the large amount of analysis and attention devoted to assessing the impacts of transient CO$_{2}$ and N in the context of global feedback loop analysis, we thus consider it a worthwhile exercise to illustrate how parametric choices in the CLM5 might affect overall behaviour in larger-scale experiments, including the controls on global carbon fertilization `$\beta$' values. We also hope to highlight areas of process and parameter uncertainty that appear to require greater attention in future model development and testing cycles.

Because of the increased number of prognostic processes with the CLM5, many alternative representations of C:N cycle interactions are possible within the same model structural space, including an effective removal of N fixation capacity (where carbon available for fixation is fixed at 0$\%$ of assimilation) and variation in the degree to which to C:N ratios are flexible. We thus consider that an exploration of the CLM5 parameter space is also equivalent to an exploration of a large part of the relevant model structural space.

\section{Methods}

\subsection{Sites}

For this experiment we utilized six different experimental sites. One in tropical forests (Caxiuan\~a), one in alpine forest (Niwot Ridge), one in temperate forest (Harvard Forest) and one in a seasonally dry evergreen forest (Metolius Forest).

\subsection{Simulation Protocol}
We spun up the default version of the model for 400 years at each site, in 'accelerated spin-up' mode (whereby the turnover of slower cycling carbon and nitrogen pools is accelerated, see (\cite{lawrence2018}) using pre-industrial CO$_{2}$ concentrations (274ppm) and recycling the available site-level half-hourly meteorological inputs. 400 years was sufficient to bring all carbon and nitrogen pools into equilibrium. Subsequent to this, parameters were perturbed (see below), and a second spin-up conducted for 180 years for each site, parameter and value combination, with accelerated mode turned off. Restarting from the state at the end of the perturbed parameter spin-ups, we ran 'control' transient simulations for each site and parameter combination starting in 1760 and invoking historical transient CO$_{2}$ and Nitrogen deposition until the end of the observed meteorological forcing.

For each site/parameter/value combination, we also ran one CO$_{2}$ and one Nitrogen deposition experiment. To allow comparison with \cite{wieder}, we increased CO$_{2}$ to 550ppm, starting in 1998. For Nitrogen, we added 5kgN $m^{-2}$/year, also starting in 1998. In line with \cite{wieder}, we assessed the impact of changes after 15 years of fertilization in both cases.

\subsection{Perturbed Physics Ensemble (PPE)}
The CLM5 has a large array of parameters that might have direct and indirect impacts on biogeochemical cycling in the CLM5. For this manuscript, we focus on parameters included in recent developments in the vegetation model, and how they might impact upon the responses to CO$_{2}$ and N fertilization. Therefore, 
we focus on parameters of particular https://www.overleaf.com/project/5b05c31494d9960223796bc3relevance to the C and N cycles and on those which are newly introduced by the modified N cycle. The choice of parameters used here is informed primarily by the model structure, as well as many iterative and informal investigations of the CLM5 model during the development process.

Our principle goal is to identify parameters that might have large impacts on responses to model forcing, as opposed to changes in the base state of the model, since these are the primary determinants of the carbon cycle feedback in the context of the Earth System Model. However, we also report responses of the model state to perturbations. Additional investigations into the parametric sensitivity of the hydrology and surface energy balance in the CLM5 are planned (Dagon et al. in prep) and into the plant hydraulics parameterizations (Kennedy et al in prep), thus, we have not included the full range of those parameters here. We expect that further focused analyses will be conducted by the CLM5 community, in tandem with analyses of coupled model experiments.

@@

\subsubsection{Parameters Selected for PPE}

The parameters included in our sensitivity analysis are both detailed in Table \ref{table_parameters}, and described in more depth below. \\

@@

5) \textbf{The fraction of carbon that can be used for fixation}, \emph{`fracfixers'}. This parameter is the fraction of the assimilation (gross primary productivity - autotrophic respiration, or $gpp$ - $R_{auto}$) that can be used for symbiotic N fixation by the FUN model, and is a proxy for the ecosystem-level fractional productivity of Nitrogen fixing plants, in lieu of, for example, a prognostic model of N fixer distributions, or an input map of their abundance, both of which could plausibly be added in future generations of CLM. \\

@@

\subsection{Parametric control over system state}

@@

For GPP, the impact of SLA is always positive, given increasing LAI, and despite higher LAI causing lower N per unit area of leaves which reduces photosynthetic capacity. The impact of SLA on NPP can however be negative (e.g., Metolius), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance. At Niwot Ridge, an optimal SLA is observed with respect to NPP, again reflecting the assimilation/respiration cost trade-off.

>>>>

\begin{document}
%tentative author list...
\authors{Rosie A. Fisher\affil{1},
William Wieder\affil{1,2},
Benjamin M. Sanderson\affil{3},
Charles D. Koven\affil{4},
Keith W. Oleson\affil{1},
Chonggang Xu\affil{5},
Joshua Fisher\aff B.il{6},
Mingjie Shi\affil{6},
Anthony P. Walker\affil{7},
Gordon B. Bonan\affil{1},
David M. Lawrence\affil{1}
}

@@

\affiliation{2}{Institute of Arctic and Alpine Research, University of Colorado, Boulder Colorado, USA}

\affiliation{3}{Centre Europe'en Research et de Formation Avenc'ee en Calcul Scientifique, Toulouse, France}

\affiliation{4}{Lawrence Berkeley National Laboratory, Berkeley, California, USA}

\affiliation{5}{Los Alamos National Laboratory, Los Alamos, New Mexico, USA}

\affiliation{6}{NASA Jet Propulsion Laboratory, Pasadena, California, USA}

\affiliation{7}{Oak Ridge National Laboratory, Oak Ridge, Tennessee, USA}

@@

\begin{keypoints}
\item The Community Land Model, version 5, contains numerous upgrades to carbon and nitrogen cycling.

\item Model state and responses to CO$_{2}$ and nitrogen addition are sensitive to parameter choice.

\item Parameters controlling nitrogen fixation, uptake, and stoichiometric flexibilty are most important
\end{keypoints}

\begin{abstract}
A suite of modifications to the nitrogen cycle representation were added to the Community Land Model, version 5.  New features of the model include prognostic $V_{c,max}$ and $J_{max}$, representation of the carbon economic cost of nitrogen uptake, switching of N uptake between alternative sources, variable tissue C:N ratios and dynamic leaf resorption of nitrogen.

Here we assess the sensitivity of the model to a suite of parameters pertinent to the cycling of carbon and nitrogen. We assess the dependence of both the model state, and also the responses of the system to CO$_{2}$ and nitrogen fertilization to parametric uncertainty. Model runs are conducted at representative individual sites in temperate, tropical and boreal systems.

The model responses to CO$_{2}$  and N fertilization are primarily linked to the representation of the fraction of plants that can fix nitrogen, the costs of N in the environment and stoichiometric flexibility of plant tissues, all of which are subject to large empirical and theoretical uncertainty.  Identification of the primary factors driving ecosystem responses to fertilization assists in the interpretation of global simulations and in the identification of priorities for fieldwork and process updates.
\end{abstract}

\section{Introduction}
Simulating the cycling of nutrients, and how nutrient availability impacts ecosystem growth and function, has been repeatedly identified as a crucial element of Earth system models (\cite{piao2013}, \cite{gruber2008}, \cite{wang2009}). In the CMIP5 multi-model inter-comparison, only one land model, the Community Land Model v4 (CLM4), included an active nitrogen (N) cycle. The CLM4 projected that inclusion of N dynamics might significantly limit the ability of the terrestrial biosphere to respond to fertilization by increasing atmospheric carbon dioxide ( \cite{friedlingstein2006}, \cite{thornton2007} \cite{friedlingstein2014}, \cite{arora2013}). Subsequent and parallel to CMIP5, many terrestrial biosphere and land surface models that represent global N dynamics using alternative structural assumptions have been developed (\cite{wang2007}, \cite{zaehle2010}, \cite{goll2012}, \cite{smith2014}). Nonetheless, substantial uncertainty remains in the land surface modeling community regarding how nutrient limitations should be represented in models (\cite{zaehledalmonech2011}).

@@

The Community Land Model is the land surface representation within the Community Earth System Model (CESM, \cite{hurrell2013}). Version 5 of the CLM was released to the research community as part of the CESM2.0 release and open-source releases and development are housed at \url{https://github.com/ESCOMP/ctsm/}. An overview of model developments is presented by \cite{lawrence2018}, a description of the global nitrogen cycling by Wieder et al. (2018), the crop model by(Lombardozzi et al. in prep), the land use components by (Lawrence P et al. in prep), and plant hydraulics by (Kennedy et al., 2018).

CLM5 includes numerous major updates of the nitrogen cycle representation relative to CLM4 and CLM4.5 (\cite{lawrence2011}). The introduction of several new dynamical features into the CLM5 has implications for both parametric uncertainty and responses to environmental forcing. Wieder et al. (2018) report the global-scale carbon cycle implications of the full model update and note that, in CLM5, carbon uptake responds more strongly to CO$_{2}$ and less strongly to N fertilization than its predecessors.  In this paper, we describe the new components of the biogeochemical cycling, and investigate the features of the new model that control the model state and biogeochemical forcing responses in depth, using single-site experiments and parametric sensitivity analyses.

\subsection{Model Updates}
The CLM5 nitrogen cycle builds on the implementation of carbon-nitrogen interactions in the CLM4 model (\cite{thornton2007}), and on modifications to the biogeochemical cycling (notably vertically stratified soil decomposition processes) included in the CLM4.5 (\cite{koven2013}, \cite{bonan2012}). The new model integrates three major additional prognostic elements of the nitrogen cycle, including:\\

1) The `LUNA' module (Leaf Utilization of Nitrogen for Assimilation), which simulates distribution of N between different leaf assimilation processes (\cite{xu2012}, \cite{ali2016}) \\

@@

3) The `FLEXCN' N cycle implementation, adapted from \cite{ghimire2016}, which is used in CLM5 primarily to allow variation in tissue C:N ratios.\\

@@

Given a specific amount of leaf N and empirical environmental constraints, the LUNA model predicts the optimal partitioning of N among the maximum rate of carboxylation $V_{c,max}$, the maximum rate of electron transport $J_{max}$, and other leaf N components, for the prevailing time-averaged environmental conditions. The model determines the rate constants that are consistent with a co-limitation of photosynthesis by both electron capture and carboxylation processes. In this fashion, $V_{c,max}$ is primarily controlled by the N per unit leaf area $N_{area}$, (which is itself a function of the target C/N ratio, the specific leaf area, and the prognostic variation in leaf C/N ratios) and prevailing environmental conditions (CO$_{2}$, temperature, humidity, soil moisture, radiation and day length). The capacity of the LUNA model to represent appropriate responses to temperature and CO$_{2}$ was assessed by \cite{xu2012} while the improved codes for global calibration and the geographical predictions of the model were described by \cite{ali2016}.

\subsubsection{FUN}
Under circumstances where insufficient N uptake was available to match all of the carbon assimilated (for a given target C:N ratio), the CLM4 model reduced the gross photosynthetic flux down to the level at which growth could be supported by N uptake. This process occurred after the calculation of stomatal conductance (which is linked to assimilation rates via the Ball-Berry model) and therefore created inconsistencies between C assimilation and water cycling, especially under conditions of N limitation, as discussed extensively in the literature (\cite{medlyn2011}, \cite{bonan2012}, \cite{dekauwe2014}, \cite{walker2014}).

One major issue confronting N cycle models is how to deal with this 'excess' carbon under N limiting conditions (\cite{zaehle2010}, \cite{dekauwe2014}). The FUN model (\cite{fisher2010fun}, \cite{brzostek2014}, \cite{shi2016}) addresses this issue by imposing the principle that for the alternative sources of nitrogen acquisition by plants (active uptake from soil, retranslocation from senescent tissues, and symbiotic N fixation) there is a concurrent cost in terms of carbon (\cite{bloom1985}, \cite{jiang2017}, \cite{terrer2018}). Further, the cost of each uptake pathway is variable in both time and space. FUN hypothesizes that plants will take up nitrogen from pathways which are 'cheaper' to them. Where N is scarce in the environment, carbon that would otherwise have been used for plant growth (net primary productivity, NPP) can be deployed to acquire (pay for) more N. Thus, N limitation leads to reduced growth and higher expenditure of C on N uptake (and reduces carbon use efficiency- defined here as NPP divided by gross primary productivity, GPP). The central element of FUN is a set of simultaneous equations which assume, firstly, that the total carbon available (after maintenance respiration and replenishment of stores are accounted for), `$C_{avail}$', is either used for plant growth ($C_{growth}$) or for nitrogen uptake, ($C_{nuptake}$).

\begin{equation}
C_{growth}=C_{avail}-C_{nuptake}
\end{equation}

Further, the nitrogen acquired from the environment ($N_{uptake}$) must equal the amount spent on N divided by it's average cost ($N_{cost}$), and also the amount of carbon deployed for growth divided by the plant C:N ratio ($CN_{plant}$):

@@

\begin{equation}
C_{nuptake} =\frac{C_{avail}}{ ( (1.0+f_{gr})*(CN_{plant} / N_{cost}) + 1) }
\end{equation}

The average nitrogen cost ($N_{cost}$) is derived from the uptake of N, weighted for its cost across all uptake streams, while the plant CN ratio ($CN_{plant}$) is the combined target CN ratio of all the plant tissues, weighted for the size of the different pools. The FUN model is documented at \url{https://escomp.github.io/ctsm-docs/doc/build/html/tech_note/FUN/CLM50_Tech_Note_FUN.html}

One mechanism introduced by FUN is the preferential use of symbiotic N fixation when soil mineral N concentrations are low (\cite{vitousek2002}). The CLM4 and CLM4.5 predict N fixation as a linear function of net primary productivity (\cite{cleveland1999}), and \cite{wieder2015} illustrated the impacts of uncertainty in this function.  FUN considers fixation rates to be an emergent property of plant assimilation rates, the relative costs of environmental N acquisition compared to fixation, and temperature (which exerts a primary control over the enzymatic processes, following \cite{houlton2008}). Fixation is preferred when the costs of `active' N acquisition from soil are higher than that of fixation.

Note that while the CLM5 has no representation of biological succession (\cite{fisher2018}), this property nonetheless affects the amount of time taken to achieve a spun-up state (carbon and nitrogen pools in equilibrium) from bare ground. In most cases, N fixation is preferred when soil N is low, and so soil N builds up quickly. In low productivity areas, however, carbon is required to fix N from a 'cold start' initial state, impacting the carbon use efficiency and survival of marginal plants; thus higher initial stocks of N are required to allow growth once metabolic and turnover costs have been met in early spin-up.

The FUN model introduces the concept of carbon payments for N uptake, which are analagous to the carbon expended on root exudates, symbiotic relationships with soil fungi, enhanced expenditure on dynaic fine root growth or increased metabolic rates to support active uptake. A more comprehensive description of these processes might include explicit representations of these processes, but the model deployed here uses a bulk approach to account for the costs to plants of low environmental N availability, therefore, uncertainties associated with the cost functions, in particular, are large.

\subsubsection{FLEXCN}
The results of FACE model-data comparison exercises illustrated that changes in the C:N ratio accounted for large changes in ecosystem carbon storage under elevated CO$_{2}$ (\cite{zaehle2014}, \cite{medlyn2015using}).  These changes were not captured by the static tissue C:N ratios used in the CLM4 and CLM4.5 nitrogen cycle. For this reason, we introduce a flexible tissue C:N ratio into the CLM5.

\cite{ghimire2016} implemented a suite of modifications to the CLM4.5 Nitrogen cycling model, including variable tissue C:N ratio, prognostic $V_{c,max}$ (resulting from this dynamic leaf N content) and also an alternative Nitrogen uptake algorithm. In the default configuration of CLM5, the LUNA model predicts $V_{c,max}$ from leaf N content (while also taking into account environmental conditions), and the FUN model represents nitrogen uptake, thus the primary element of CLM5 utilized from the \cite{ghimire2016} model is the modification to the allocation scheme that allows tissue C:N ratios to be modified in response to varying N supply. In the new allocation algorithm, the total nitrogen supply in each timestep is partitioned between tissues in proportion to their relative 'demand' terms (ascertained from the target C:N ratio and the carbon allocated to the pool).  The carbon allocation scheme uses a fixed-fraction approach to allocation in general, with constant ratios between, leaf, fine roots, stem and coarse root allocation. We note here that the carbon allocation scheme is thus capable of generating physiologically sub-optimal leaf area index values, for example, with some of the canopy in negative carbon balance, an issue which must be taken into account during simulations under high productivity conditions.

\subsubsection{Adaptation of FUN to flexible CN ratios}
The FUN model was originally conceived with a static tissue C:N ratio, and will by default allocate an amount of carbon to N uptake that exactly tracks the target C:N ratio. In CLM5, one of the aims of the development process was to incorporate a varying C:N ratio, as above. To that end, it is necessary to modify the amount of C expended on N uptake (and thus the amount of N required). The degree to which tissue C:N content varies as N becomes limiting is unclear in the literature, and N cycle models typically include heuristic representations of tissue N adjustments under N limited conditions (including \cite{zaehle2010},\cite{ghimire2016}). Here we include a placeholder algorithm that adapts to 1) the environmental cost of N acquisition and 2) the degree to which the plant is already far from its target N content. When N is expensive in the environment, less C is spent on uptake, increasing C:N ratios where N is scarce. When plants become extremely N limited, however, expenditure increases again to prevent CN ratios becoming unrealistically high. This new algorithm is also documented in the CLM5 technical description ((\url{(https://escomp.github.io/ctsm-docs/doc/build/html/tech_note/index.html)}) and includes three tuning parameters ($flexcn_{a}$, $flexcn_{b}$ \& $flexcn_{c}$) the sensitivity of which is investigated here.

\subsection{Content of this paper}
In this paper, we assess in detail the sensitivity of the CLM5 model parameterization of ecosystem biogeochemistry. We use a range of single site experiments, combined with one-at-a-time parameter uncertainty analyses from the default state, as well as CO$_{2}$ and N fertilization experiments, to fully investigate the performance of the model under steady-state and step-change modifications in forcing.

Given the large amount of analysis and attention devoted to assessing the impacts of transient CO$_{2}$ and N in the context of global feedback loop analysis, we thus consider it a worthwhile exercise to illustrate how parametric choices in the CLM5 might affect and be responsible for overall behaviour in larger-scale simulations, including the controls on global carbon fertilization `$\beta$' values  (the change in ecosystem carbon storage in response to CO$^{2}$ fertilization). We also hope to highlight areas of process and parameter uncertainty that appear to require greater attention in future model development and testing cycles. {CXU: Will it possible to propose some key hypotheses here for easier guidance of the paper?}

Because of the increased number of prognostic processes {CXU: probabily put the total number of parameter for CLM5 here} with the CLM5, many alternative representations of C:N cycle interactions are possible within the same model structural space, including an effective removal of N fixation capacity (where carbon available for fixation is fixed at 0$\%$ of assimilation), variation in the degree to which to C:N ratios are flexible, and the ease with which plants may used carbon resources to more efficiently exploit available soil N. Thus, the parameter space explored here represents a reasonable fraction of the relevant model structural space.

\section{Methods}
\subsection{Sites}
For this experiment we utilized four different observational flux tower sites to capture a range of initial conditions, across tropical evergreen broadleaf forest (Caxiuan\~a, -1.9$^{o}$N, -51.4$^o}$E),  sub-alpine evergreen forest (Niwot Ridge, 40.3$^{o}$N, -105.4$^{o}$E), temperate deciduous broadleaf forest (Harvard Forest, 42.5$^{o}$N -72.2$^{o}$E) and seasonally dry evergreen needleleaf forest (Metolius Forest, 44.5$^{o}$N -121.6$^{o}$E).  These sites are all flux tower sites, and all have previously been used for model development.  Each site was driven with the available meteorological data (\textit{give date ranges of met data}). Soil texture, color, depth and, plant functional type composition were taken from previous model validation exercises undertaken at these sites (\cite{bonan2012} for Metolius and Harvard Forest, \cite{fisher2007} for Caxiuan\~a and ?  for Niwot Ridge.

\subsection{Simulation Protocol}
We spun up the default version of the model for 400 years at each site, in 'accelerated spin-up' mode (whereby the turnover of slower cycling carbon and nitrogen pools is increased for the duration of the spin-up, and the pool sizes are modified accordingly at the end of the spin-up - see (\cite{lawrence2018}). We used pre-industrial CO$_{2}$ concentrations (274ppm) and recycling the available site-level half-hourly meteorological inputs. 400 years was sufficient to bring all soil and vegetation carbon and nitrogen pools into equilibrium. Subsequent to this, parameters were perturbed (see below), and a second spin-up conducted for 180 years for each site, parameter and value combination, with accelerated mode turned off. Restarting from the state at the end of the perturbed parameter spin-ups, we ran 'control' transient simulations for each site and parameter combination starting in 1760 and invoking historical transient CO$_{2}$ and Nitrogen deposition until the end of the observed meteorological forcing.

For each site/parameter/value combination, we also ran one CO$_{2}$ and one nitrogen deposition simulation. To allow comparison with \cite{wieder}, we increased CO$_{2}$ to 550ppm, starting in 1998. For Nitrogen, we added 5gN $m^{-2}$/year, also starting in 1998. Similar to \cite{wieder}, we assessed the impact of changes after 15 years of fertilization in both cases.

\subsection{Perturbed Physics Ensemble (PPE)}
The CLM5 has a large array of parameters that might have direct and indirect impacts on biogeochemical cycling in the model. For this manuscript, we focus on parameters included in developments in the vegetation model, and how they might impact upon the responses to CO$_{2}$ and N fertilization. Therefore, we focus on parameters of particular relevance to the C and N cycles and on those which are newly introduced by the modified N cycle. The choice of parameters used here is informed primarily by the model structure, as well as many iterative and informal investigations of the CLM5 model during the development process. 
Our principle goal is to identify parameters that might have large impacts on responses to model forcing, as opposed to changes in the base state of the model, since these are the primary determinants of the carbon cycle feedback in the context of the Earth system model. However, we also report responses of the model state to perturbations. Additional investigations into the parametric sensitivity of the hydrology and surface energy balance in the CLM5 are planned (Dagon et al. in prep) and into the plant hydraulics parameterizations (Kennedy et al in review), thus, we have not included the full range of those parameters here. We expect that further focused analyses will be conducted by the CLM5 community, in tandem with analyses of coupled model experiments.

@@

\subsubsection{Parameters selected for perturbation experiment}
The parameters included in our sensitivity analysis are both detailed in Table \ref{table_parameters}, and described in more depth below. \\

@@

5) \textbf{The fraction of carbon that can be used for fixation}, \emph{`fracfixers'}. This parameter is the fraction of the assimilation (gross primary productivity - autotrophic respiration, or $gpp$ - $R_{auto}$) that can be used for symbiotic N fixation by the FUN model, and is a proxy for the ecosystem-level fractional productivity of nitrogen fixing plants, in lieu of, for example, a prognostic model of N fixer distributions, or an input map of their abundance, both of which could plausibly be added in future generations of CLM. \\

@@

\subsection{Parametric control over system state}
{CXU: I do not like the report of list of sensitivity. Instead it would be helpful to make a nice story based on hypothesis in the introductions to stich all these element together}

@@

For GPP, the impact of SLA is always positive, given increasing LAI and despite higher LAI causing lower N per unit area of leaves which reduces photosynthetic capacity. The impact of SLA on NPP can however be negative (e.g., Metolius), since the fixed-fraction allometry model in CLM5 can generate shaded leaves that are in negative carbon balance. At Niwot Ridge, an optimal SLA (or local maximum at the second-largest parameter values) is observed with respect to NPP, again reflecting the assimilation/respiration cost trade-off.
